---
title: "extra"
author: "Keith Hultman"
date: "12/16/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is code that did not make it into the final cut...



## Modeling: decision tree

Another type of modeling that will help in WNV classification is decision trees. Adding this type of model will help to connect non-linear relationships among the predictors. 

```{r, eval=FALSE, include=FALSE}
suppressMessages(library(C50))

trainC50df <- train %>% select(WnvPresent, geo.hot.cl, Species, nrows, Summer, WeekAvgMos, Tmin, WetBulb, ResultSpeed, ma10, precip3d, precip5d, precip10d)

trainC50df$WnvPresent <- as.factor(trainC50df$WnvPresent)
save(trainC50df, file = "./data/trainC50df.RData")

c50m <- C5.0(WnvPresent ~., data = trainC50df, trials = 1)
trainpredict <- predict(c50m, newdata = train, type = "prob")
?C5.0

roc1 <- roc(train$WnvPresent, trainpredict[,2])
auc(roc1)

summary(c50m)

test$C50.Wnv.pred <- predict(c50m, newdata = test, type = "prob")
```

Every prediction is the same for this classifier...

## Data understanding: WNV presense

I next wanted to examine more closely the distribution of WNV presence throughout the season. For each Year-Week-Trap combination, compute the ratio of WNV presense to total tests. Then graph the distribution with Weeks as the dependent variable.

```{r}

YWT_ratio <- train %>% group_by(Year, Week, Trap) %>% summarise(WnvPresent_ratio = sum(WnvPresent)/(sum(WnvPresent)+sum(!WnvPresent)))
hist(YWT_ratio$WnvPresent_ratio)
ggplot(YWT_ratio, aes(x=Week, y=WnvPresent_ratio)) + geom_jitter() + ggtitle("Ratio of WNV over Weeks") + stat_smooth()

W_ratio <- train %>% group_by(Week) %>% summarise(WnvPresent_ratio = sum(WnvPresent)/(sum(WnvPresent)+sum(!WnvPresent)))
hist(W_ratio$WnvPresent_ratio)
ggplot(W_ratio, aes(x=Week, y=WnvPresent_ratio)) + geom_jitter() + ggtitle("Ratio of WNV over Weeks") + stat_smooth()

W_count <- train %>% group_by(Week) %>% summarise(WnvPresent_count = sum(WnvPresent))
ggplot(W_count, aes(x=Week, y=WnvPresent_count)) + geom_jitter() + ggtitle("Count of WNV over Weeks") + stat_smooth()

W_count_loess <- loess(WnvPresent_count ~ Week, data = W_count)
# plot residuals
plot(W_count_loess$residuals)

W_count_loess$fitted
```

## Modeling:

I would like to incorporate the above distribution, which looks approxiamately normal throughout the season. 

## Evaluation: 


## Modeling 4: Random Forest

```{r}
suppressMessages(library(randomForest))
train$WnvPresent <- as.factor(train$WnvPresent)
train$geo.hot.cl <- as.factor(train$geo.hot.cl)
rf <- randomForest(WnvPresent ~ nrows+geo.hot.cl+Tavg+Tmin+WetBulb+ResultSpeed+ma5+ma10+precip5d,
                   data = train, ntree = 500, mtry = 3)
rf


```
